Enhancing the prediction of sales for newly published books by means of computational intelligence methods

### 2016-05-05 paper.tex
Question for @amorag
More questions for @amorag
Fixed typo in tree label and reduced table size
More questions for @amorag re: UMatrix
And more stuff for @amorag
More comments from reviewer #3 for @amorag
Reviewing state of the art pt. I

Specifically, time-series prediction methods
\cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990}  
is perhaps the most used technique to tackle the sales forecasting
problems. The efficiency of these techniques strongly depends on the field of application 
and the correctness of the problem data. However, since they require a
large amount of data for predicting sales, these methods are not the
most suitable for this task \cite{ChingChin2010}. And they cannot be
applied before the book is published, as is the objective of this paper.

@@

For this reason, usually the methods used to predict book sales have
been generally based on experts' experience.% Reference - JJ
 They analyse data about
sales and, taking into account their knowledge in industry, their
experience, and their perception about trends, could make decisions on
the companies production, i.e. how many books should be printed when a new
book is published. 
This is a complex problem, since the predictions are influenced by
external variables that must be taken into account, such as
seasonality, promotions or fashions that expert managers might
subjectively apply \cite{Lapide1999,ChernWSF15}. % This
                                % has something to do with the
                                % previous paragraph? Put it there!!! 
%
  %[pedro] sobre la industria editorial no hay trabajos sobre predicción de ventas.
  % Lo habitual ha sido usar el conocimiento de expertos para realizar predicciones 
  %  o aconsejar acerca de la cantidad de libros a imprimir.
  % Lo más parecido que he encontrado son dos trabajos (uno en realidad) de Moon et al. 
  %  sobre "Use Blog Information As Book Sales Prediction":
  %     Moon2010ICSSSM
  %     Moon2010ICEC
Recently, some works have proposed analysing relationships between on-line information 
and book sales \cite{Moon2010ICSSSM,Moon2010ICEC}. Specifically, Moon
et al. propose using the number of blog references as an indicator of
the success of a book, and thus, its sales. Different sales patterns
are observed by analysing data obtained. 
% Antonio - describir esos 'sales patterns'. ;)
% FERGU: y también cuales son esos 'data obtained'
However, the authors used in these papers historical data from published books, 
so their proposed methodology can not be applied to the problem of unpublished-books sales prediction.
%FERGU: pero nosotros también usamos historical data, no? qué diferencia hay con lo nuestro? por qué lo nuestro es lo mejor?

@@

The SOM algorithm is applied with a large map size of $26 \times 16$  in order to represent the data. The best SOM training results are obtained with a final quantisation error of 0.691 and topographic error of 0.046.

Figure \ref{fig:componentplanes} shows the U-matrix and component
variables resulted from SOM training. The term component is used in
SOM to refer to the features. The component planes in Figure
\ref{fig:componentplanes} show the trend of values of the prototype
vectors of the SOM map units. These values are represented as
colours. The colorbar on the right of each component plane shows the
indication of each colour. On the other side, the U-matrix on the top
left corner shows the distances between the adjacent units. It is
important to note that high values in the matrix indicates large
distance between the units of the map. It can be noticed also that
there are more hexagons in the U-matrix than component planes since
the distances between units is also represented as hexagons.

>>>>

Specifically, time-series prediction methods
\cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990}  
is perhaps the most used technique to tackle sales forecasting
problems. The efficiency of these techniques strongly depends on the field of application 
and the correctness of the problem data. However, since they require a
large amount of data for predicting sales, these methods are not the
most suitable for this task \cite{ChingChin2010}. And they cannot be
applied before the book is published, as is the objective of this paper.

@@

For this reason, usually the methods used to predict book sales have
been generally based on experts' experience.% Reference - JJ
 They analyse data about
sales and, taking into account their knowledge of industry, their
experience, and their perception about trends, could make decisions on
the companies production, i.e. how many books should be printed when a new
book is published. 
This is a complex problem, since the predictions are influenced by
external variables that must be taken into account, such as
seasonality, promotions, or fashions that expert managers might
subjectively apply \cite{Lapide1999,ChernWSF15}. % This
                                % has something to do with the
                                % previous paragraph? Put it there!!! 
%
  %[pedro] sobre la industria editorial no hay trabajos sobre predicción de ventas.
  % Lo habitual ha sido usar el conocimiento de expertos para realizar predicciones 
  %  o aconsejar acerca de la cantidad de libros a imprimir.
  % Lo más parecido que he encontrado son dos trabajos (uno en realidad) de Moon et al. 
  %  sobre "Use Blog Information As Book Sales Prediction":
  %     Moon2010ICSSSM
  %     Moon2010ICEC
Recently, some works have proposed analysing relationships between on-line information 
and book sales \cite{Moon2010ICSSSM,Moon2010ICEC}. Specifically, Moon
et al. propose using the number of blog references as an indicator of
the success of a book, and thus, its sales. Different sales patterns
are observed by analysing data obtained. 
% Antonio - describir esos 'sales patterns'. ;)
% FERGU: y también cuales son esos 'data obtained'
However, the authors used in these papers historical data from published books, 
so their proposed methodology can not be applied to the problem of unpublished books sales prediction.
%FERGU: pero nosotros también usamos historical data, no? qué diferencia hay con lo nuestro? por qué lo nuestro es lo mejor?

@@

The SOM algorithm is applied with a large map size of $26 \times 16$
in order to represent the data. % Not enough justification. Did you
                                % try others? - jj
 The best SOM training results are obtained with a final quantisation
 error of 0.691 and topographic error of 0.046. % explain what is
                                % quantisation and topographic error
                                % and why it is important - JJ

Figure \ref{fig:componentplanes} shows the U-matrix and component
variables resulted from SOM training. The term component is used in
% really, are you reading this with the mind of someone that has no
% idea what is SOM or U-Matrix or whatever? Tell first what you are
% going to do, then tell why you are doing it, explain all the
% terminology and then show the results. You can't keep saying "I have
% done this and this is the result. You have to explain why you are
% doing it, what you are doing, how you are doing it and then how to
% interpret the results - JJ
SOM to refer to the features. %use features!!!! - JJ
 The component planes in Figure %what is a plane? Really, you don't
                                %know what's in the mind of the reader
                                %(or reviewer#3, who is a son of a
                                %bitch - JJ
\ref{fig:componentplanes} show the trend of values of the prototype
vectors of the SOM map units. These values are represented as
colours. The colorbar on the right of each component plane shows the
indication of each colour. On the other side, the U-matrix on the top
left corner shows the distances between the adjacent units. It is
important to note that high values in the matrix indicates large
distance between the units of the map. It can be noticed also that
there are more hexagons in the U-matrix than component planes since
the distances between units is also represented as hexagons. % but
                                % explain that at the beginning!
                                % Devote one or two paragraphs to tell
                                % the reader what is U-Matrix, a
                                % reference, why we are using it and
                                % how it conveys more information that
                                % a pure and simple feature selection
                                % (which we are doing anyway). If we
                                % don't, Reviewer #3 (who is,
                                % remember, a son of a bitch) will
                                % tell you to just suppress that whole
                                % section - JJ
